Teaching Dossier

### 2020-02-24 CUT/teaching-philosophy.tex
Teaching report appendices section headers

\appendix
\section*{Appendices}
%Observation Reports
%Extended Abstract for Research paper
%Full evaluations
%Sample Lesson Plan from guest lecture
%Sample Assignment from CO 327
%Sample Lesson Plan from CO 327
\section{Teaching Observation Report 1}\label{sec:observation-report-1}
\begin{tabular}{r l}
\textbf{Event Observed:}&	CO-456: Introduction to Game Theory\\
\textbf{Date Observed:}&	November 23, 2018\\
\textbf{Location:}&	E2-1732\\
\textbf{Time:}&	11:30 am - 12:20 pm\\
\textbf{Number of Students Present:}&	39\\
\textbf{Observer:}&	Shahrukh Athar, Graduate Instructional Developer,\\
     &University of Waterloo Centre for Teaching Excellence\\
\end{tabular}

@@

When writing on the whiteboard, it is important not to talk as your back is turned to your audience. This creates a disconnect between the teacher and the learners. For example, a student may have their hand raised to signal to the instructor that they want to ask a question, but if the instructor is not looking towards the students then they can easily miss taking that question. This also leads to the loss of eye contact, which is an important aspect of interpersonal communication as it signals interest in others and helps in classroom management (such as preventing students from getting distracted from the material). I noted that you talked while writing on the board several times during the lesson. For example, when you were discussing different cases, you were almost continuously writing on the board and talking at the same time. In your future teaching opportunities, try to incorporate the Write-Turn-Talk technique, where you should write on the board first without talking, then turn towards the learners and talk while looking at them. Doing so will enable you to better engage the students into the learning process and will help you in keeping a bird’s eye view of the class.\newline
\textbf{Additional Comments:}
Thank you for having me in this class for your lesson, Justin! It was a pleasure to observe your teaching. I wish you nothing but the best in all your future teaching endeavors.
\section{Teaching Observation Report 2}\label{sec:observation-report-2}
\begin{tabular}{r l}
    \textbf{Event Observed:}&	CO327: Deterministic OR Models\\
    \textbf{Date Observed:}&	July 16, 2019\\
    \textbf{Location:}&	RCH 206\\
    \textbf{Time:}&	10:00am – 11:00am\\
    \textbf{Number of Students Present:}&	8\\
    \textbf{Observer:}&	Caelan Wang, Graduate Educational Developer,\\
         &University of Waterloo Centre for Teaching Excellence
\end{tabular}

>>>>

\appendix
\section*{Appendices}
%Observation Reports
%Extended Abstract for Research paper
%Full evaluations
%Sample Lesson Plan from guest lecture
%Sample Assignment from CO 327
%Sample Lesson Plan from CO 327
\section{Teaching Observation Report 1}\label{sec:observation-report-1}
\emph{The teaching report presented below has been condensed from its original form in the interest of space.}

\begin{tabular}{r l}
\textbf{Event Observed:}&	CO-456: Introduction to Game Theory\\
\textbf{Date Observed:}&	November 23, 2018\\
\textbf{Location:}&	E2-1732\\
\textbf{Time:}&	11:30 am - 12:20 pm\\
\textbf{Number of Students Present:}&	39\\
\textbf{Observer:}&	Shahrukh Athar, Graduate Instructional Developer,\\
     &University of Waterloo Centre for Teaching Excellence\\
\end{tabular}

@@

When writing on the whiteboard, it is important not to talk as your back is turned to your audience. This creates a disconnect between the teacher and the learners. For example, a student may have their hand raised to signal to the instructor that they want to ask a question, but if the instructor is not looking towards the students then they can easily miss taking that question. This also leads to the loss of eye contact, which is an important aspect of interpersonal communication as it signals interest in others and helps in classroom management (such as preventing students from getting distracted from the material). I noted that you talked while writing on the board several times during the lesson. For example, when you were discussing different cases, you were almost continuously writing on the board and talking at the same time. In your future teaching opportunities, try to incorporate the Write-Turn-Talk technique, where you should write on the board first without talking, then turn towards the learners and talk while looking at them. Doing so will enable you to better engage the students into the learning process and will help you in keeping a bird’s eye view of the class.
\section{Teaching Observation Report 2}\label{sec:observation-report-2}
\emph{The teaching report presented below has been condensed from its original form in the interest of space.}

\begin{tabular}{r l}
    \textbf{Event Observed:}&	CO327: Deterministic OR Models\\
    \textbf{Date Observed:}&	July 16, 2019\\
    \textbf{Location:}&	RCH 206\\
    \textbf{Time:}&	10:00am – 11:00am\\
    \textbf{Number of Students Present:}&	8\\
    \textbf{Observer:}&	Caelan Wang, Graduate Educational Developer,\\
         &University of Waterloo Centre for Teaching Excellence
\end{tabular}
